Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-21 manuscript.Rmd
class level table

>>>>

\renewcommand{\arraystretch}{.75}
```{r metricsbyclass}
metrics_class <- read_csv("data/group_split_metrics_class.csv") %>% 
  filter(model %in% c("group", "split")) %>% 
  mutate(Model = factor(model, levels = c("group", "split"), labels = c("Group", "Individual")))

metrics_long_class <- metrics_class %>% pivot_longer(cols = `Balanced Accuracy`:Kappa, 
                                         names_to = "metric",
                                         values_to = "value")

metrics_long_summary <- metrics_long_class %>% group_by(Class,Model, metric) %>% 
  get_summary_stats(value) %>% 
  select(-(variable:max), -(q1:mad), -se, -ci) %>% 
  pivot_wider(names_from = Model, values_from = c("median", "mean", "sd")) %>% 
  filter(metric != "Neg Pred Value", metric != "Specificity") %>% 
  relocate(mean_Group, .after = median_Group) %>% 
  relocate(sd_Group, .after = mean_Group) %>% 
  mutate(across(-(Class:metric), ~ apa_num(.x, digits = 3)),
         metric = factor(metric, levels = metric_labels),
         Class = factor(Class, levels = c("Supine", "Prone", "Sitting", "Upright", "Held"))) %>% 
  relocate(metric, .before = Class) %>% 
  arrange(metric, Class)

class_table <- metrics_long_summary %>% mutate(metric = as.character(metric))
class_table$metric[duplicated(class_table$metric)] <- " "

apa_table(class_table, col.names = c("Metric","Position", "Median", "Mean", "SD", "Median", "Mean", "SD"), col_spanners = list("Group" = c(3, 5), "Individual" = c(6, 8)),
          midrules = c(5, 10, 15, 20),
          caption = "Model performance metrics for each body position class, shown separately for group and individual models.")
```

### 2023-02-21 manuscript.tex
exemplar timeline
class level table

@@

>>>>

{\centering \includegraphics[width=0.9\linewidth]{figures/timeline}

\caption{Example Timeline Caption.}\label{fig:exemplartimeline}
\end{figure}

@@

\renewcommand{\arraystretch}{.75}

\caption{\label{tab:metricsbyclass}Summary statistics for model performance metrics shown separately for group and individual models.}

\begin{tabular}{llllllll}
\toprule
 &  & \multicolumn{3}{c}{Group} & \multicolumn{3}{c}{Individual} \\
\cmidrule(r){3-5} \cmidrule(r){6-8}
Metric & Position & Median & Mean & SD & Median & Mean & SD\\
\midrule
Balanced Accuracy & Supine & 0.977 & 0.935 & 0.099 & 0.995 & 0.957 & 0.090\\
 & Prone & 0.997 & 0.950 & 0.110 & 0.983 & 0.921 & 0.132\\
 & Sitting & 0.932 & 0.861 & 0.151 & 0.973 & 0.943 & 0.071\\
 & Upright & 0.930 & 0.867 & 0.146 & 0.937 & 0.877 & 0.123\\
 & Held & 0.907 & 0.872 & 0.111 & 0.892 & 0.854 & 0.153\\ \midrule
F1 & Supine & 0.952 & 0.873 & 0.173 & 0.987 & 0.937 & 0.130\\
 & Prone & 0.965 & 0.923 & 0.124 & 0.958 & 0.889 & 0.186\\
 & Sitting & 0.897 & 0.805 & 0.247 & 0.963 & 0.927 & 0.101\\
 & Upright & 0.781 & 0.748 & 0.235 & 0.868 & 0.769 & 0.227\\
 & Held & 0.813 & 0.783 & 0.163 & 0.862 & 0.786 & 0.240\\ \midrule
Sensitivity & Supine & 1.000 & 0.945 & 0.125 & 1.000 & 0.948 & 0.141\\
 & Prone & 1.000 & 0.907 & 0.216 & 0.988 & 0.856 & 0.266\\
 & Sitting & 0.901 & 0.787 & 0.291 & 0.977 & 0.917 & 0.136\\
 & Upright & 0.878 & 0.767 & 0.275 & 0.893 & 0.790 & 0.255\\
 & Held & 0.867 & 0.774 & 0.229 & 0.817 & 0.722 & 0.309\\ \midrule
Pos Pred Value & Supine & 0.973 & 0.802 & 0.300 & 1.000 & 0.939 & 0.131\\
 & Prone & 0.991 & 0.896 & 0.196 & 0.993 & 0.901 & 0.197\\
 & Sitting & 0.910 & 0.840 & 0.238 & 0.967 & 0.947 & 0.078\\
 & Upright & 0.848 & 0.743 & 0.285 & 0.875 & 0.817 & 0.205\\
 & Held & 0.917 & 0.803 & 0.247 & 0.949 & 0.872 & 0.232\\ \midrule
Kappa & Supine & 0.932 & 0.770 & 0.307 & 0.984 & 0.913 & 0.169\\
 & Prone & 0.951 & 0.887 & 0.208 & 0.948 & 0.851 & 0.242\\
 & Sitting & 0.836 & 0.712 & 0.308 & 0.946 & 0.889 & 0.134\\
 & Upright & 0.729 & 0.700 & 0.277 & 0.829 & 0.744 & 0.232\\
 & Held & 0.786 & 0.733 & 0.219 & 0.845 & 0.744 & 0.280\\
\bottomrule
\end{tabular}
